Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-30 latex/appendix.tex
tex

	\item [*] 7-step PGD and better aligned comparison: compare when
		these methods reach similar retrieval performance.

@@

>>>>

	\item [*] 7-step PGD (as well as 16-step PGD) and better aligned comparison:
		compare when these methods reach similar retrieval performance.
		Meanwhile we can do experiments much faster.

@@

	\item [?] Combine and even better. | Mixing ACT and AMDsemi does result
		in clearly better results. It's on par with AMDsemi.

### 2021-09-30 latex/robdml.tex
tex

Given a set of data points, a metric gives a distance value between each pair
of them, while Deep Metric Learning (DML) aims to learn such a metric
leveraging the representational power of deep neural networks.
%
DML has been extensively studied~[], and has a wide range of applications
such as image retrieval~[] and face recognition~[].

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation is proposed for the adversarial training
		of triplet-based deep metric learning models, which avoids model
		collapse in the typical min-max adversarial training setting.
		\oo{We discover that blah}.
		Our proposed method achieves higher adversarial robustness compared
		to the state-of-the-art.
		%
	\item Combine and even better.
		%
	\item Accelerate and reduce the cost for reproducing and applying.
		%
\end{enumerate}

@@

>>>>

Given a set of data points, a metric gives a distance value between each pair
of them.
%
Deep Metric Learning (DML) aims to learn such a metric between two inputs (\eg,
images) leveraging the representational power of deep neural networks.
%
DML has been extensively studied~[], and has a wide range of applications such
as image retrieval~[] and face recognition~[].

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation is proposed for the adversarial training
		of triplet-based deep metric learning models, which avoids model
		collapse in the typical min-max adversarial training setting.
		\oo{We discover that blah}.
		Our proposed method achieves higher adversarial robustness compared
		to the state-of-the-art.
		%
\end{enumerate}

@@

1. hardness manipulation, comparison with state-of-the-art.
